---
title: "UN Report on the Relationship Between C02 Emissions, GDP, and Life Expectancy"
author: "Alberto Correa III"
date: "1-18-2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include = FALSE}
library(tidyverse)
library(ggprism)
library(knitr)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read-data, include = FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

```{r gdp-lifeExp-1997-plot, echo = FALSE, fig.align='center', fig.width=8, fig.height=5}
# Make plot of GDP vs. LifeExp
ggplot(data = gapminder_1997)+ 
         aes(x = gdpPercap , y = lifeExp, color = continent)+
         labs(x = "GDP per capita", y = "Life Expectancy")+
         geom_point()+
         theme_prism()+
         scale_color_brewer(palette = "Set1")
```


```{r basic-country-stats}
# No of countries in dataset
nCountries <- 
  gapminder_1997%>%
  select(country)%>%
  n_distinct()

#minimum GDP calculations
minGDP <- gapminder_1997%>%
  summarize(round(min(gdpPercap)))%>%
  pull()

#maximum GDP calculations
maxGDP <- gapminder_1997%>%
  summarize(round(max(gdpPercap)))%>%
  pull()
```

The number of countries in the dataset is `r nCountries`.
The minimum GDP is `r minGDP`.
The maximum GDP is `r maxGDP`.

```{r table}
gapminder_1997%>%
  filter(continent == "Oceania")%>%
  kable()
```



